DATA 624 Homework 9

### 2020-04-21 DATA624/HW9.Rmd
Finalizing HW 9

```{r}
library(AppliedPredictiveModeling)
data(ChemicalManufacturingProcess)

@@

```{r}
set.seed(42)
bagControl = bagControl(fit = ctreeBag$fit, predict = ctreeBag$pred, aggregate = ctreeBag$aggregate)
bag_model <- train(Yield ~ ., data = train_df, method="bag", bagControl = bagControl,
                   center = TRUE,
                   scale = TRUE,
                   trControl = trainControl("cv", number = 10),
                   tuneLength = 25)
bag_predictions <- predict(bag_model, test_df)
bag_in_sample <- merge(bag_model$results, bag_model$bestTune)
results <- data.frame(t(postResample(pred = bag_predictions, obs = test_df$Yield))) %>%
  mutate("In Sample RMSE" = bag_in_sample$RMSE,
         "In Sample Rsquared" = bag_in_sample$Rsquared,
         "In Sample MAE" = bag_in_sample$MAE,
         "Model"= "Bagged Tree") %>%
  rbind(results)
bag_model
```
#### Boosted Tree

```{r}
set.seed(42)
gbm_model <- train(Yield ~ ., data = train_df, method="gbm", verbose = FALSE,
                   trControl = trainControl("cv", number = 10),
                   tuneLength = 25)
gbm_predictions <- predict(gbm_model, test_df)
gbm_in_sample <- merge(gbm_model$results, gbm_model$bestTune)
results <- data.frame(t(postResample(pred = gbm_predictions, obs = test_df$Yield))) %>%
  mutate("In Sample RMSE" = gbm_in_sample$RMSE,
         "In Sample Rsquared" = gbm_in_sample$Rsquared,
         "In Sample MAE" = gbm_in_sample$MAE,
         "Model"= "Boosted Tree") %>%
  rbind(results)
gbm_model
```

@@

```{r}
set.seed(42)
rf_model <- train(Yield ~ ., data = train_df, method = "ranger", 
                  scale = TRUE,
                  trControl = trainControl("cv", number = 10),
                  tuneLength = 25)
rf_predictions <- predict(rf_model, test_df)
rf_in_sample <- merge(rf_model$results, rf_model$bestTune)
results <- data.frame(t(postResample(pred = rf_predictions, obs = test_df$Yield))) %>%
  mutate("In Sample RMSE" = rf_in_sample$RMSE,
         "In Sample Rsquared" = rf_in_sample$Rsquared,
         "In Sample MAE" = rf_in_sample$MAE,
         "Model"= "Random Forest") %>%
  rbind(results)
rf_model
```

@@

```{r}
set.seed(42)
crf_model <- train(Yield ~ ., data = train_df, method = "cforest",
                   trControl = trainControl("cv", number = 10),
                   tuneLength = 25)
crf_predictions <- predict(crf_model, test_df)
crf_in_sample <- merge(crf_model$results, crf_model$bestTune)
results <- data.frame(t(postResample(pred = crf_predictions, obs = test_df$Yield))) %>%
  mutate("In Sample RMSE" = crf_in_sample$RMSE,
         "In Sample Rsquared" = crf_in_sample$Rsquared,
         "In Sample MAE" = crf_in_sample$MAE,
         "Model"= "Conditional Random Forest") %>%
  rbind(results)
crf_model
```

@@

```{r}
results %>%
  arrange(RMSE) %>%
  kable() %>%
  kable_styling()
```

@@

```{r}
varImp(bag_model)
```

@@

```{r}
varImp(pls_model)
```

@@

```{r}
set.seed(1)
cart_model <- train(Yield ~ ., data = train_df, method = "rpart",
                    trControl = trainControl("cv", number = 10),
                    tuneLength = 25)
fancyRpartPlot(cart_model$finalModel, sub="")
```

>>>>

```{r 8_7_A_pls}
library(AppliedPredictiveModeling)
data(ChemicalManufacturingProcess)

@@

```{r 8_7_A_bag}
set.seed(42)
bagControl = bagControl(fit = ctreeBag$fit, predict = ctreeBag$pred, aggregate = ctreeBag$aggregate)
bag_model <- train(Yield ~ ., data = train_df, method="bag", bagControl = bagControl,
                   center = TRUE,
                   scale = TRUE,
                   trControl = trainControl("cv", number = 10),
                   tuneLength = 25)
bag_predictions <- predict(bag_model, test_df)
bag_in_sample <- merge(bag_model$results, bag_model$bestTune)
results <- data.frame(t(postResample(pred = bag_predictions, obs = test_df$Yield))) %>%
  mutate("In Sample RMSE" = bag_in_sample$RMSE,
         "In Sample Rsquared" = bag_in_sample$Rsquared,
         "In Sample MAE" = bag_in_sample$MAE,
         "Model"= "Bagged Tree") %>%
  rbind(results)
bag_model
```
#### Boosted Tree

```{r 8_7_A_gbm}
set.seed(42)
gbm_model <- train(Yield ~ ., data = train_df, method="gbm", verbose = FALSE,
                   trControl = trainControl("cv", number = 10),
                   tuneLength = 25)
gbm_predictions <- predict(gbm_model, test_df)
gbm_in_sample <- merge(gbm_model$results, gbm_model$bestTune)
results <- data.frame(t(postResample(pred = gbm_predictions, obs = test_df$Yield))) %>%
  mutate("In Sample RMSE" = gbm_in_sample$RMSE,
         "In Sample Rsquared" = gbm_in_sample$Rsquared,
         "In Sample MAE" = gbm_in_sample$MAE,
         "Model"= "Boosted Tree") %>%
  rbind(results)
gbm_model
```

@@

```{r 8_7_A_rf}
set.seed(42)
rf_model <- train(Yield ~ ., data = train_df, method = "ranger", 
                  scale = TRUE,
                  trControl = trainControl("cv", number = 10),
                  tuneLength = 25)
rf_predictions <- predict(rf_model, test_df)
rf_in_sample <- merge(rf_model$results, rf_model$bestTune)
results <- data.frame(t(postResample(pred = rf_predictions, obs = test_df$Yield))) %>%
  mutate("In Sample RMSE" = rf_in_sample$RMSE,
         "In Sample Rsquared" = rf_in_sample$Rsquared,
         "In Sample MAE" = rf_in_sample$MAE,
         "Model"= "Random Forest") %>%
  rbind(results)
rf_model
```

@@

```{r 8_7_A_crf}
set.seed(42)
crf_model <- train(Yield ~ ., data = train_df, method = "cforest",
                   trControl = trainControl("cv", number = 10),
                   tuneLength = 25)
crf_predictions <- predict(crf_model, test_df)
crf_in_sample <- merge(crf_model$results, crf_model$bestTune)
results <- data.frame(t(postResample(pred = crf_predictions, obs = test_df$Yield))) %>%
  mutate("In Sample RMSE" = crf_in_sample$RMSE,
         "In Sample Rsquared" = crf_in_sample$Rsquared,
         "In Sample MAE" = crf_in_sample$MAE,
         "Model"= "Conditional Random Forest") %>%
  rbind(results)
crf_model
```

@@

```{r 8_7_A_results}
results %>%
  arrange(RMSE) %>%
  kable() %>%
  kable_styling()
```

@@

```{r 8_7_B_bag}
varImp(bag_model)
```

@@

```{r 8_7_B_pls}
varImp(pls_model)
```

@@

```{r 8_7_C}
set.seed(1)
cart_model <- train(Yield ~ ., data = train_df, method = "rpart",
                    trControl = trainControl("cv", number = 10),
                    tuneLength = 25)
fancyRpartPlot(cart_model$finalModel, sub="")
```
